My Findings

### 2024-09-04 Findings (Shared Folder)/Chapters/MolecularBiology.tex
new notes added

\section{Important Random Facts}

@@

	 the apparent viscosity in large vessels matches the in vitro result, but the apparent viscosity is substantially higher than the in vitro estimate in smaller vessels. For example, the estimated apparent viscosity in a $7\mu m$ capillary at hematocrit $45$ percent is about $8.4\mu_p$, almost seven times higher than would be expected based on data from glass tubes.

>>>>

\section{Important Facts}

@@

	 the apparent viscosity in large vessels matches the in vitro result, but the apparent viscosity is substantially higher than the in vitro estimate in smaller vessels. For example, the estimated apparent viscosity in a $7\mu m$ capillary at hematocrit $45\%$ is about $8.4\mu_p$, almost seven times higher than would be expected based on data from glass tubes.
	 \item An important implication of the existence of the endothelial surface layer is that the endothelial cell membrane does not experience a significant level of fluid shear stress due to plasma flow over its surface. Instead, shear stress is transmitted to the endothelial cells via the attachment points of the macromolecules that anchor the ESL, including syndecans and glypicans [23, 24]. Being transmembrane proteins, these molecules may in turn transmit the shear stress to the internal cytoskeleton, consistent with an important role for the cytoskeleton in mechanotransduction of shear stress [25, 26] \cite{Secomb2021}.
	 \item However, when the flow of blood is considered, additional complexity arises because blood is a concentrated suspension of cells, whose dimensions are comparable to microvessel diameters. As mentioned earlier, red blood cells show a tendency to migrate away from microvessel walls. The fluid mechanical mechanisms underlying this behavior depend on the deformability of the cells and on the fluid dynamical interactions of cells with the walls and are only partially understood [18, 28,29,30,31,32,33]. The distribution of red blood cells across the vessel cross-section affects the distribution of hematocrit in each branch when the flow reaches a diverging microvascular bifurcation [34], and the theoretical understanding of this phenomenon is a challenging problem in the low Reynolds number flow [35,36,37] \cite{Secomb2021}.
	 \item Transport of oxygen is a critical function of the circulation. Being a non-polar molecule, it has relatively low solubility in water and in tissue \cite{Secomb2021}.
	 \item Therefore, it must be delivered by convective transport within such a distance of all cells that require oxygen. This requires a dense network of tiny vessels throughout the tissue. On the other hand, viscous resistance to blood flow is very high in vessels with very small diameters. For mechanical efficiency, the vascular system must include hierarchical branching structures feeding the microvessels, such that convective transport over larger distances can be achieved by vessels with larger diameters and lower resistance to flow. In effect, the vascular system must solve a complex patterning problem, generating a structure in which a dense meshwork of capillaries is combined with a hierarchical structure of arteries, arterioles, venules, and veins of varying lengths and diameters so that all parts of the tissues are adequately supplied with blood flow [40] \cite{Secomb2021}.
	 \item A quick anatomy: Blood vessels are mainly formed by endothelial cells (ECs) and mural cells (MCs). ECs are responsible for the exchange and barrier functions of the vascular network. MCs, which are in close contact with the ECs, contribute to vessel stability. Vessels with a large caliber (arteries and veins) are sheltered by vascular smooth muscle cells (vSMCs) while capillaries are covered by pericytes (PCs) (Potente and Mäkinen, 2017; van Dijk et al., 2015) \cite{Ouarne2021}.
	 \item lood vessels develop by distinct mechanisms (Semenza, 2007). First, vasculogenesis forms the primary vascular plexus by a de novo production of ECs from the mesoderm (Kolte et al., 2016; Potente and Mäkinen, 2017). Then, vascular networks grow through angiogenesis, a process responsible for the formation of new blood vessels from pre-existing ones (Potente and Mäkinen, 2017) \cite{Ouarne2021}.
	 \item Angiogenesis can occur by two different mechanisms: i) sprouting angiogenesis, characterized by the expansion of pre-existing vascular networks into a web of interconnected capillaries; and ii) intussusceptive angiogenesis, characterized by the formation of an intussusceptive pillar, splitting and remodeling of blood vessels \cite{Ouarne2021}.
	 \item Vessel pruning plays a crucial role in optimizing blood flow within immature vascular networks, contributing to their hierarchical organization. This process involves the selective removal of superfluous or non-perfused vessels. Unlike vascular involution, vessel pruning does not rely on endothelial cell (EC) death. Instead, it depends on the migration and rearrangement of ECs in response to blood flow (Fonseca et al., 2020; Potente et al., 2011). In fact, only 5 to 15\% of vessels undergoing pruning contain apoptotic ECs (Franco et al., 2015; Y. Zhang et al., 2018b) \cite{Ouarne2021}.
	 \item This is a dynamic process of structural adaptation and flow regulation that continually adjusts the vessel caliber to compensate for heterogeneity, leading to a flow redistribution according to metabolic needs to ensure adequate tissue oxygenation (Roy and Secomb, 2020) \cite{Ouarne2021}.
	 \item Vascular quiescence stabilizes the vascular network by halting its development, allowing endothelial cells (ECs) to specialize and mural cells (MCs) to mature into their specific organ functions. During quiescence, ECs stop proliferating and migrating (Ricard et al., 2021), creating a balanced state supported by mature MCs. However, this equilibrium is not permanent; quiescence can be disrupted during various physiological processes, such as pregnancy and the menstrual cycle (Carmeliet, 2005; Ricard et al., 2021), as well as in pathological conditions (see Section 6) \cite{Ouarne2021}.
	 \item where $ \rho $ is the “resistivity”, which is supposed to be the same for all the pipes. For $ m = 1 $, the flow in each channel is pluglike (e.g., electric current in metallic wire, liquid flow in porous conduct,…), while for $ m=2 $, the flow is Poiseuille-like (e.g., laminar viscous flow in pipe)\cite{Durand2006}.
	 \item Therefore, it may be of interest to compare the structure of some natural networks with the results presented in this work. Indeed, it has been already shown in various publications [22,23] that Murray’s law is well satisfied in some appropriate portions of human and animal vascular systems. In that case, the flow profile is nearly Poiseuille-like ($ m=2 $) and the relevant constraint is a fixed total channel volume ($ n=1 $) [22,23] \cite{Durand2006}.
